Fivebranes

### 2022-03-16 fivebranes/index.tex
minor edits

The index we compute will have four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
  \item $q$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}

A convenient choice of choice of weights is as in the following table:

\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & 1 & 0 & -1 & 0 & 0 \\
  $t_{2}$ & 0 & 1 & -1 & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & -1 \\
  $q$ & -1 & -1 & -1 & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\end{center}

\begin{prop}
  The $\SU(3)\times \SU(2)\times U(1)$ character of the large $N$ local operators of the M5 brane theory is given by

  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}q+t_{1}t_{2}^{-1}q+t_{2}q+r^{-1}q^{-3/2}+rq^{-3/2} \\  - & t_{1}q^{-1}-t_{1}^{-1}t_{2}q^{-1}-t_{2}^{-1}q^{-1}-rq^{3/2}-r^{-1}q^{3/2}
          \end{aligned}\right)}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}\right ).\]
  \end{prop}

>>>>

We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra $\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)$ which embeds in the following way:

\begin{itemize}
\end{itemize}

This is the image of the subalgebra chosen in the calculation in \ref{} via under the map $E(3|6)\to E(5|10)$ discussed in \surya{earlier}

The equivariant character thus has four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ again denote generators for the Cartan of $\lie{sl}(3)$ acting by vector fields on $\C^{3}_{z}$.
  \item $r$ denotes a generators for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on the normal directions $\C_{w}$.
  \item $q$ denotes a generator for the cartan of additional $\lie{gl}(1)$ acting by a divergence free vector field on $\C^{5}$ that restricts to a dilation on $\C^{3}$.
\end{itemize}

This choice of subalgebra is such that it restricts to the choice made in

The convenient choice of weights is summarized in the following table:
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & 1 & 0 & -1 & 0 & 0 \\
  $t_{2}$ & 0 & 1 & -1 & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & -1 \\
  $q$ & -1 & -1 & -1 & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\end{center}
\parsec

\begin{prop}
  The character of local operators of the holomorphic twist of the theory on a large number of fivebranes is given by the following plethystic exponential

  \[ \rm PExp [f_{large N}(t_{1}, t_{2}, q, r)] \]

  where the single particle index is \[f_{large N}(t_{1}, t_{2}, q, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1}+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
\end{prop}

\parsec The specialization of this index in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
\[
f_{two}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q)^{2}.
\]

This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.

\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $\rm AdS_{7}\times S^{4}$ \surya{...}
